My title

### 2024-11-21 paper/paper.qmd
update model

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

>>>>

The variables in the two datasets contains the following:

- Geographical Information: Longitude (x) and Latitude (y), with corresponding identifiers for location (Station Name in @tbl-raw-climate, station_id and province in @tbl-raw-ahccd).
- Temperature Metrics: Mean, maximum, and minimum temperatures (Mean Temp, Mean Max Temp, Mean Min Temp, Extr Max Temp, Extr Min Temp) and associated flags for data validity in @tbl-raw-climate. Similar metrics (temp_mean, temp_max, temp_min) in @tbl-raw-ahccd, with additional units included.
- Precipitation and Snowfall: Total precipitation (Total Precip) and total snow (Total Snow), with flags for data quality in @tbl-raw-climate. Equivalent precipitation and snow variables (total_precip, snow) in @tbl-raw-ahccd, with units explicitly defined.
- Wind and Gust Metrics: Direction and speed of maximum gusts (Dir of Max Gust, Spd of Max Gust) in @tbl-raw-climate, with units and flags. Wind speed (wind_speed) and related metrics in @tbl-raw-ahccd, with units included.
- Pressure Information: Sea level and station pressure variables in @tbl-raw-ahccd (pressure_sea_level, pressure_station) with units.
- Temporal Information: Date and time variables (Date/Time in @tbl-raw-climate, date, period_value in @tbl-raw-ahccd) to track observations across time periods.
- Flags and Identifiers: Flags for data validity in both tables, such as precipitation flags, temperature flags, and identifiers like Climate ID or identifier.

## Data Cleaning

###
